---
title: "Analyzing Benchmark Logs"
author: "Yixuan Qiu"
date: "`r Sys.Date()`"
# output: html_document
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

# Parsing Log Data

```{r message=FALSE}
library(jsonlite)
library(dplyr)

# Read log
dat = readLines("logs/run_20230503.log")
# Remove messages other than data
dat = grep("^[{}]|^  ", dat, value = TRUE)
# Make the log a legal JSON file
dat = gsub("}", "},", dat)
last_bracket = tail(grep("},", dat), 1)
dat[last_bracket] = "}"
dat = c("[", dat, "]")
# Some null values are actually infinity, so we replace them with a large value
dat = gsub("null", "1e300", dat)

# Parse JSON
dat = parse_json(dat)
dat = do.call(rbind, lapply(dat, as_tibble))

# Clean data
dat = dat %>% filter(flag != 2) %>%
    mutate(fail = flag) %>%
    select(alg, problem, nvar, solver, fail, niter, nfun,
           objval, proj_grad, solve_time, msg) %>%
    mutate(niter = ifelse(fail, NA, niter),
           nfun = ifelse(fail, NA, nfun),
           objval = ifelse(fail, NA, objval),
           proj_grad = ifelse(fail, NA, proj_grad),
           solve_time = ifelse(fail, NA, solve_time * 1000)) %>%
    mutate(fail = ifelse(fail, "<span style=\"color:red\">1</span>", "0"))
```

# L-BFGS Solvers

The variables in the table are as follows:

1. `problem`: Name of the optimization problem.
2. `nvar`: Number of variables of the problem.
3. `solver`: The solver used. "Classic" stands for the Fortran code.
4. `fail`: Whether the solver fails on a specific problem. Some objective functions are indeed ill-posed or ill-conditioned.
5. `niter`: Number of iterations of an algorithm.
6. `nfun`: Number of function evaluations used.
7. `objval`: The final objective function value.
8. `proj_grad`: The final (projected) gradient norm.
9. `solve_time`: Running time of the solver, in milliseconds.
10. `msg`: Error messages.

```{r}
library(DT)
lbfgs = dat %>% filter(alg == "L-BFGS") %>% select(-alg)
opts = list(pageLength = 20, scrollX = TRUE, autoWidth = TRUE,
            columnDefs = list(list(width = "300px", targets = ncol(lbfgs) - 1)))
datatable(lbfgs, options = opts, rownames = FALSE, escape = FALSE) %>%
    formatSignif(columns = c("objval", "proj_grad", "solve_time"),
                 digits = 5, interval = 999)
```

# L-BFGS-B Solvers

```{r}
lbfgsb = dat %>% filter(alg == "L-BFGS-B") %>% select(-alg)
datatable(lbfgsb, options = opts, rownames = FALSE, escape = FALSE) %>%
    formatSignif(columns = c("objval", "proj_grad", "solve_time"),
                 digits = 5, interval = 999)
```
